The \dealii Library, Version 9.1

### 2019-06-04 9.1/paper.tex
Remove an old funding acknowledgement
Reply to Wolfgang's comment

GPU support was significantly extended for the current release:
\begin{itemize}
  \item The \texttt{CUDAWrappers::PreconditionILU} and \texttt{CUDAWrappers::PreconditionIC}
    classes can now be used for preconditioning \texttt{CUDAWrappers::SparseMatrix} objects.
  \item \texttt{LinearAlgebra::distributed::Vector}: the MPI-parallel vector
    class has gained a second template argument \texttt{MemorySpace} which can
    either be \texttt{Host} or \texttt{CUDA}. In the latter case, the data
    resides in GPU memory. By default, the template parameter is
    \texttt{Host} and the behavior is unchanged compared to previous versions.
    When using CUDA, the ghost exchange can be performed either by first copying
    the relevant data to the host, performing MPI communication, and finally
    move the data to the device or, if CUDA-aware MPI is available, by
    performing MPI communication directly between GPUs.
  \item Constrained degrees of freedom: the matrix-free framework now
    supports constrained degrees of freedom. The implementation is based on the algorithms described in
    \cite{ljungkvist2017}. With this addition, both Dirichlet
    boundary conditions and the constraints arising from adaptively
    refined meshes can be imposed within the matrix-free framework. The only restriction is that for two-dimensional meshes the
    finite element degree must be odd.  
    \marginpar{Can we explain this restriction? It seems odd (pun intended)...}
    There is no such restriction in three
    dimensions.
  \item MPI matrix-free computations: using \texttt{LinearAlgebra::distributed::Vector}, the
    matrix-free framework can scale to multiple GPUs by taking
    advantage of MPI. Each MPI process can only use one GPU and therefore, if
    multiple GPUs are available in one node, it is necessary to have as many
    ranks as there are GPUs. Using Nvidia Multi-Process Service (MPS), it is also possible
    for multiple processes to use the same GPU. This can be advantageous if the
    amount of work on one rank is not sufficient to fully utilize a GPU.
\end{itemize}

@@

J-P.~Pelteret was supported by the European Research Council (ERC) through
the Advanced Grant 289049 MOCOPOLY.

>>>>

GPU support was significantly extended for the current release:
\begin{itemize}
  \item The \texttt{CUDAWrappers::PreconditionILU} and \texttt{CUDAWrappers::PreconditionIC}
    classes can now be used for preconditioning \texttt{CUDAWrappers::SparseMatrix} objects.
  \item \texttt{LinearAlgebra::distributed::Vector}: the MPI-parallel vector
    class has gained a second template argument \texttt{MemorySpace} which can
    either be \texttt{Host} or \texttt{CUDA}. In the latter case, the data
    resides in GPU memory. By default, the template parameter is
    \texttt{Host} and the behavior is unchanged compared to previous versions.
    When using CUDA, the ghost exchange can be performed either by first copying
    the relevant data to the host, performing MPI communication, and finally
    move the data to the device or, if CUDA-aware MPI is available, by
    performing MPI communication directly between GPUs.
  \item Constrained degrees of freedom: the matrix-free framework now
    supports constrained degrees of freedom. The implementation is based on the algorithms described in
    \cite{ljungkvist2017}. With this addition, both Dirichlet
    boundary conditions and the constraints arising from adaptively
    refined meshes can be imposed within the matrix-free framework. The only restriction is that for two-dimensional meshes the
    finite element degree must be odd.  
    \marginpar{Can we explain this restriction? It seems odd (pun intended)...}
    \marginpar{BT: No, we cannot. I have spent at least two full weeks trying to
    understand why it doesn't work, i.e., gives the wrong result, but I don't know. We decided at the time that
    even with the current limitation this was a useful addition.}
    There is no such restriction in three
    dimensions.
  \item MPI matrix-free computations: using \texttt{LinearAlgebra::distributed::Vector}, the
    matrix-free framework can scale to multiple GPUs by taking
    advantage of MPI. Each MPI process can only use one GPU and therefore, if
    multiple GPUs are available in one node, it is necessary to have as many
    ranks as there are GPUs. Using Nvidia Multi-Process Service (MPS), it is also possible
    for multiple processes to use the same GPU. This can be advantageous if the
    amount of work on one rank is not sufficient to fully utilize a GPU.
\end{itemize}

@@
